Self Regulation Ontology Retest Data Report

### 2017-03-28 SRO_Report.Rmd
working in report

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T))}
```

@@

Spearman correlations for surveys are noticably higher than task reliabilities.
```{r warning=FALSE, message=FALSE}
ggplotly(cor_df %>%
  ggplot(aes(spearman, fill=task, label=dv))+
  geom_histogram(alpha=0.5, position='identity')+
  theme_bw()+
  theme(legend.title = element_blank()))
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T))}
```

@@

Spearman correlations for surveys are noticably higher than task reliabilities.

```{r echo=FALSE}
get_labels = function(plot_df, ref_df, bin_col, group_col){

  plot_df$bin = as.numeric(factor(plot_df$x))
  ref_df$bin = NA

  for(i in 1:nrow(ref_df)){
    for(j in 1:nrow(plot_df)){
      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
        ref_df$bin[i] <- plot_df$bin[j]
      }
    }
  }

  ref_df = ref_df %>% 
    group_by(bin, task) %>%
    mutate(label=as.character(toJSON(unique(dv))))

  label_df = ref_df[!duplicated(ref_df[,c('label')]),c('task', 'bin', 'label')]

  out_df = left_join(plot_df,label_df, by= c("bin", "task"))

  return(out_df)
}

line_break <- function(cell){
  out = paste(unlist(strsplit(gsub("\\]","",gsub("\\[","",cell)), ",")), sep="\n", collapse = "</br>")
  return(out)
}

prettify_label = function(df){
  for(i in 1:nrow(df)){
    df$label[i] =line_break(df$label[i])
  }
  return(df)
}
```

```{r warning=FALSE, message=FALSE}
ggplotly(ggplot_build(cor_df %>%
                        ggplot(aes(spearman, fill=task)) +
                        geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
           mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
           get_labels(.,cor_df, "spearman", "task") %>%
           prettify_label(.) %>%
           ggplot(aes(x,y, fill=task, label=label))+
           geom_bar(stat='identity', position='identity', alpha=0.5)+
           xlab('Spearman')+
           ylab('Count')+
           theme_bw(),
         tooltip = 'label',
         hoverinfo = 'text')
```
